### 2014-11-09 store-opsem.tex
Cleaned up proofs

\begin{theorem}[Soundness Modulo Classification]
\label{thm:weak-soundness}
For every well-formed execution state $\E$, and contract class $\tau 
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \pll \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv_{\tau}[\eff/\cureff]$
\end{theorem}
\begin{proof}
  By case analysis on $(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
  \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
  \langle s,i,\sigma \rangle \pll \Sigma')$. 
  \GK{Lets first finalize all notations, rules, and also agree on
  all theorem statements. This way we don't have to change the proof
  again.} 
\end{proof}

\begin{corollary}[Soundness]
\label{thm:soundness}
For every well-formed execution state $\E$, and contract class $\tau
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
contract $\cv$ in the contract class $\tau$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \pll \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
Follows from Theorems~\ref{thm:classification-sound} and
\ref{thm:weak-soundness}
\qed
\end{proof}

>>>>

First, we prove a useful lemma:

\input{auxred-wf-proof}

We now define causal consistency property of the store formally:

\begin{definition}
  A store $\Theta$ is said to be causally consistent under an execution
  $\E=\Exec$ if and only if:
  \begin{smathpar}
  \begin{array}{cr}
    \hspace*{-0.5in}\forall (r\in{\sf dom}(\Theta)). \forall (\eff \in
      \Theta(r)). & \\
    \hspace*{0.3in}\forall (a\in \EffSoup). \hbo{a}{\eff} \Rightarrow a 
      \in \Theta(r) & H\npp \\
  \end{array}
  \end{smathpar}
  Where, $\hboZ = (\Rvis \cup \Rso)^{+}$
\end{definition}

The following theorem proves that our operational semantics correctly
enforce $\ecc$, $\ccc$, and $\scc$ guarantees:

% Main Theorem
% ------------
\input{soundness-theorem-proof}

We now show that every configuration of the store that is reachable
via the reduction relation ($\xrightarrow{}$) is causally consistent.

\input{causal-consistency-proof}

\begin{corollary}[Soundness]
  \label{thm:soundness}
  For every well-formed execution state $\E$, for every store $\Theta$
  that is causally consistent under $\E$, for every contract class $\tau
  \in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
  contract $\cv$ in the contract class $\tau$, If:
  \begin{smathpar}
  (\E, \Theta, \langle s,i,op_\tau :: 
  \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
  \langle s,i+1,\sigma \rangle \pll \Sigma)
  \end{smathpar}
  then (\romannumeral 1) $\E'$ is well-formed, (\romannumeral 2)
  $\Theta'$ is causally consistent under $\E'$, and (\romannumeral 3)
  $\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
  Follows from Theorems \ref{thm:classification-sound},
  \ref{thm:local-state-is-cc}, and \ref{thm:weak-soundness}.
  \qed
\end{proof}
